---
output:
  pdf_document: default
  html_document: default
---
# Oyster Landings Figures  
  
This data set is manually updated by the oyster landings data located here: https://public.myfwc.com/FWRI/PFDM/ReportCreator.aspx.  The Commercial Fisheries Landings Summaries allows the user to select the date year range and oysters (as the Species).  

The Suwannee counties used in these figures are TAYLOR, DIXIE, and LEVY.  
The Apalachicola counties used iin these figures are FRANKLIN and WAKULLA.  
  
  
The State of Florida data are all of the counties in Florida where oysters are landed, and this is selected in the FWC Commercial Fisheries Landings Summaries website.  


```{r landings_options setup, include=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("cowplot")
library("ggplot2")
library("ggpubr")
library("grid")
library("gridExtra")
library("lattice")
library("marelac")
library("scales")
library("ggpubr")
library("tidyverse")
```
  
```{r ,include=FALSE, warning=FALSE, message=FALSE, comment=FALSE}
startYear = 1986
endYear = as.numeric(format(Sys.Date(), "%Y"))


### Reading in the csv
county_landings<- read.csv("data/oys_landings/ReportCreatorResults-County.csv", header= T, skip = 9)


### Manipulating the county data to only display Apalachicola Counties
apalach <- county_landings %>% 
  filter (County.Landed== "FRANKLIN" | County.Landed=="WAKULLA")%>%
  select(Year, Pounds, Trips) %>% 
  group_by(Year) %>% 
  mutate(pounds_sum= sum (Pounds)) %>% 
  mutate(trips_sum= sum (Trips)) %>% 
  mutate (per_trip= pounds_sum/trips_sum) %>% #<- calculating per trips
  filter (! duplicated(Year)) %>% 
  rename ("Landings (lbs)"= pounds_sum, "Total Trips"= trips_sum, "CPUE"= per_trip) %>% 
  gather(value, measurement, c("Landings (lbs)", "Total Trips", "CPUE")) %>% 
  group_by (Year, value) %>% 
  summarise(measurement=measurement) %>% 
  add_column(area= "Apalachicola")

apalach_df<- data.frame(apalach)

### Manipulating the county data to only display Suwannee Counties
suwannee <- county_landings %>% 
  filter (County.Landed== "TAYLOR" | County.Landed=="DIXIE" | County.Landed=="LEVY") %>% #<- filtering out counties
  select(Year, Pounds, Trips) %>% 
  group_by(Year) %>% 
  mutate(pounds_sum= sum (Pounds)) %>% 
  mutate(trips_sum= sum (Trips)) %>% 
  mutate (per_trip= pounds_sum/trips_sum) %>% #<- calculating per trips
  filter (! duplicated(Year)) %>% 
  rename ("Landings (lbs)"= pounds_sum, "Total Trips"= trips_sum, "CPUE"= per_trip) %>% 
  gather(value, measurement, c("Landings (lbs)", "Total Trips", "CPUE")) %>% 
  group_by (Year, value) %>% 
  summarise(measurement=measurement) %>% 
  add_column(area= "Suwannee Sound")

suwannee_df<- data.frame(suwannee)

### Manipulating the county data to only display all Counties
state <- county_landings %>% 
  select(Year, Pounds, Trips) %>% 
  group_by(Year) %>% 
  mutate(pounds_sum= sum (Pounds)) %>% 
  mutate(trips_sum= sum (Trips)) %>% 
  mutate (per_trip= pounds_sum/trips_sum) %>% #<- calculating per trips
  filter (! duplicated(Year)) %>% 
  rename ("Landings (lbs)"= pounds_sum, "Total Trips"= trips_sum, "CPUE"= per_trip) %>% 
  gather(value, measurement, c("Landings (lbs)", "Total Trips", "CPUE")) %>% 
  group_by (Year, value) %>% 
  summarise(measurement=measurement) %>% 
  add_column(area= "State")

state_df<- data.frame(state)

### Merging all dataframes for easy facet_wrapping, needed to be in data.frame for rbind to function

all_landings <- rbind(apalach_df, suwannee_df, state_df)

all_landings<- all_landings %>% 
  na.omit(value) %>% 
  na.omit(area)

all_landings$area<- factor(all_landings $area,levels=c ("Apalachicola", "Suwannee Sound", "State"))
all_landings$value<- factor(all_landings$value,levels=c ("Landings (lbs)", "Total Trips", "CPUE"))

```
  
```{r echo= FALSE,warning=FALSE, message=FALSE, comment=FALSE, fig.width= 7, fig.height= 8}
  ggplot(all_landings, aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(startYear:endYear), labels= seq(from = startYear, to = endYear, by = 1)) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme(legend.position = "top",
    axis.text.x = element_text(angle=90, hjust = 0.5), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
      panel.background = element_blank(),
      panel.grid.major = element_blank(), 
      panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 
```
  
**Figure 6-1.** Figure of oyster landings (lbs), total trips, and cost per unit effort (CPUE) for Apalachicola (blue line), Suwannee Sound (orange), and the State of Florida (pink) for years `r startYear` to `r endYear`.  
  
```{r echo=FALSE, fig.width= 7, fig.height= 8}
all_landings %>% 
  filter(Year > 2011) %>% 
  filter(!(area== "State")) %>% 
ggplot(aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3.5) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(2012:endYear)) +
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90, hjust = 0), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 

```
  
**Figure 6-2.** Figure of oyster landings (lbs), total trips, and cost per unit effort (CPUE) for Apalachicola (blue line), Suwannee Sound (orange) for years 2012 to `r endYear`.  
  
  
```{r, echo=FALSE, fig.width= 7, fig.height= 8}
all_landings %>% 
  filter(Year> 2014) %>% 
  filter(!(area== "State")) %>% 
  ggplot(aes(x= as.numeric(Year), y= as.numeric(measurement))) +
  geom_line (aes(color= area), size= 1.2) +
  geom_point(aes(color= area), size=3.5) +
  xlab("Year") +
  ylab("") +
  labs(color= "Area") +
  scale_linetype_manual(values = c('solid','dotted', 'longdash')) + 
  scale_y_continuous(labels = function(x) format(x, scientific = FALSE)) +
  scale_color_manual(values= c("#0072B2", "#D55E00", "#CC79A7")) +
  scale_x_continuous (breaks= c(2015:endYear)) +
  #xlim(2015,2020) +
  theme(legend.position = "top",
        axis.text.x = element_text(angle=90, hjust = 1), 
        panel.border = element_rect(colour = "black", fill=NA,size=1, linetype="solid"), 
        strip.text = element_text(size=15),
        text = element_text(size=15),
        axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  facet_wrap(~value , scales="free_y", ncol= 1) 

```
  
**Figure 6-3.** Figure of oyster landings (lbs), total trips, and cost per unit effort (CPUE) for Apalachicola (blue line), Suwannee Sound (orange) for years 2015 to `r endYear`.  
  
